Contextual Combinatorial Cascading Bandits

### 2016-01-29 contextual combinatorial cascading bandits.tex
update

@@

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper forces the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar recommendation model of cascading bandits with position discounts, where all users are characterized into different classes and each item has a class-specific "reward". 
\wei{So, does that mean \cite{combes2015learning}, comparing to ours, only lacks of contextual
	information? or it our reward function is also more general? It is not very clear to me.}
In our setting, users and items are represented by general feature vectors.
Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

\wei{please cite the arxiv version below}
\citet{chen2013combinatorial} consider general reward functions and probabilistic triggering of base arms
	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
Cascading bandits can be viewed as a particular type of probabilistic triggering, where
	only the head of the list is deterministically triggered and all the remaining items are
	probabilistically triggered.
However, their work does not consider contextual information, and it is also difficult to
	incorporate position discounts in a general triggering model.

@@

\wei{"large discount is more important" sounds weird. Usually large discount means cheaper and less
	important products. 
Perhaps we should seriously consider not using "position discount". It is a position weight, but
since weight is already used, we should call it something else. Perhaps "position factor"? 	
}

@@

@@

Our setting generalizes several existing works but not limited to them. For example, in medical treatment, a patient will be recommended with a series of treatments. The patient has to take the treatments one by one, so the series of treatment actually is a list. Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$. $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment. We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$. So a treatment $a$ is successful with probability
\begin{equation}
\label{eq:betaTau}
1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
\end{equation}
where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number. We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful. So the expected reward function is
$$
f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
$$
where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.

>>>>

\shuai{Our proofs build on previous work but also generalize their proof in our setting. Two challenges have been dealt with, partial observability on contextual bandits and general reward function with position discounts.  }

@@

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper forces the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar recommendation model of cascading bandits with position discounts, where all users are characterized into different classes and each item has a class-specific "reward". 
\wei{So, does that mean \cite{combes2015learning}, comparing to ours, only lacks of contextual
	information? or it our reward function is also more general? It is not very clear to me.}
\shuai{They dealt with discounted 'or' reward. At each time, suppose the user is from class $c$, then recommending her with $K$ items from item-class $h(c)$. We have more general reward function and more general context information.}
In our setting, users and items are represented by general feature vectors.
Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

\wei{please cite the arxiv version below}
\citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
Cascading bandits can be viewed as a particular type of probabilistic triggering, where
	only the head of the list is deterministically triggered and all the remaining items are
	probabilistically triggered.
However, their work does not consider contextual information, and it is also difficult to
	incorporate position discounts in a general triggering model.

@@

\wei{"large discount is more important" sounds weird. Usually large discount means cheaper and less
	important products. 
Perhaps we should seriously consider not using "position discount". It is a position weight, but
since weight is already used, we should call it something else. Perhaps "position factor"? 	
}
\shuai{What if I change this part by 'large $\gamma_k$'?}

@@

\shuai{There is no experiment with an approximation oracle. But if we want to add some experiment beyond our setting, maybe we can keep it.}

@@

Our setting generalizes several existing works but not limited to them.
If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in

in medical treatment, a patient will be recommended with a series of treatments. The patient has to take the treatments one by one, so the series of treatment actually is a list. Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$. $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment. We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$. So a treatment $a$ is successful with probability
\begin{equation}
\label{eq:betaTau}
1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
\end{equation}
where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number. We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful. So the expected reward function is
$$
f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
$$
where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.
